QPLIB: A Library of Quadratic Programming Instances

### 2016-12-07 QPLIB-3.tex
Added pics

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{./pics/pic_overview.png}
  \caption{...\label{fig:1}}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{./pics/pic_var_small.png}
  \caption{...\label{fig:4}}
\end{figure}

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{./pics/pic_var_medium.png}
  \caption{...\label{fig:3}}
\end{figure}

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{./pics/pic_var_big.png}
  \caption{...\label{fig:2}}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{./pics/pic_constr_small.png}
  \caption{...\label{fig:5}}
\end{figure}

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{./pics/pic_constr_medium.png}
  \caption{...\label{fig:6}}
\end{figure}

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{./pics/pic_constr_big.png}
  \caption{...\label{fig:7}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{./pics/pic_quad_vs_convex_constr.png}
  \caption{...\label{fig:8}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{./pics/pic_fuffa.png}
  \caption{...\label{fig:9}}
\end{figure}

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{./pics/pic_density.png}
  \caption{...\label{fig:10}}
\end{figure}

\begin{figure}\centering
  \includegraphics[width=0.85\textwidth]{./pics/pic_neg_eig.png}
  \caption{...\label{fig:10}}
\end{figure}
